\LARGE \bf Expectation-Maximization based defense mechanism for distributed Model Predictive Control

### 2022-01-31 article/article.tex
correct first line
add graph for dmpc exchange

% \loop\iftrue%
\errmessage{This article is copyrighted by ___ and should not be TeXed}%
\repeat%

@@

\begin{equation}
  \label{eq:thetaNegot}
\thetai\pplusone=\thetai\p+\rho\left(\vec{\lambda}_{i}^{\star} (\vec{\theta}_{i}\p)-I_{c}^{M} \pseudoinv{I_{c}^{M}}\vec{\lambda}^{\star} (\vec{\theta}\p)\right)
\end{equation}
\todo[verify if need to use max]{
\begin{equation}
  % \label{eq:thetaNegot}
  \thetai\pplusone=
  \left\{ \thetai\p+\rho\left(\vec{\lambda}_{i}^{\star} (\vec{\theta}_{i}\p)-I_{c}^{M} \pseudoinv{I_{c}^{M}}\vec{\lambda}^{\star} (\vec{\theta}\p)\right)
  ,0\right\}
\end{equation}
}
where ${I_{c}^{M}=\kron{\1_{M,1}}{I_{c}}}$.
\todo{Observe that ${I_{c}^{M} \pseudoinv{I_{c}^{M}}\vec{v}=\frac{\sum_{i=0}^{M}\vec{v}_{i}}{M}}$}

\todo{
  The coordinator must also assure that ${\thetaik\succeq\0}$ so the local problems are feasible.
  But observe in~\eqref{eq:projectedSubgradient} that if ${\vec{\theta}_{i}\p=\0}$, ${(\vec{\lambda}_{i}^{\star} (\vec{\theta}_{i}\p)-I_{c}^{M} \pseudoinv{I_{c}^{M}}\vec{\lambda}^{\star} (\vec{\theta}\p))}$ needs to be negative so $\vec{\theta}_{i}\pplusone$ becomes negative, which is impossible \question{is it though?} since $\lambdaik\succeq\0$, from the KKT optimality conditions, seen in~\cite[Chapter 5]{BoydVandenberghe2004}.
}

>>>>

\loop\iftrue%
\errmessage{This article is copyrighted by ___ and should not be TeXed}%
\repeat%

@@

\begin{equation}
  \label{eq:thetaNegot}
\thetai\pplusone=\thetai\p+\rho\left(\vec{\lambda}_{i}^{\star} (\vec{\theta}_{i}\p)-I_{c}^{M} \pseudoinv{I_{c}^{M}}\vec{\lambda}^{\star} (\vec{\theta}\p)\right)
\end{equation}
\todo[verify if need to use max]{
\begin{equation}
  % \label{eq:thetaNegot}
  \thetai\pplusone=
  \left\{ \thetai\p+\rho\left(\vec{\lambda}_{i}^{\star} (\vec{\theta}_{i}\p)-I_{c}^{M} \pseudoinv{I_{c}^{M}}\vec{\lambda}^{\star} (\vec{\theta}\p)\right)
  ,0\right\}
\end{equation}
}
\no{\todo[delete probably]{
  But observe in~\eqref{eq:projectedSubgradient} that if ${\vec{\theta}_{i}\p=\0}$, ${(\vec{\lambda}_{i}^{\star} (\vec{\theta}_{i}\p)-I_{c}^{M} \pseudoinv{I_{c}^{M}}\vec{\lambda}^{\star} (\vec{\theta}\p))}$ needs to be negative so $\vec{\theta}_{i}\pplusone$ becomes negative, which is impossible \question{is it though?} since $\lambdaik\succeq\0$, from the KKT optimality conditions, seen in~\cite[Chapter 5]{BoydVandenberghe2004}.
}}

% TODO(accacio): correct image
\begin{figure}[h]
  \centering
  \begin{tikzpicture}[node distance=1.7cm]
    \tikzset{
      agent/.style={draw,circle,minimum width=1cm,},
      coord/.style={draw,circle,minimum width=1.7cm,very thick}
    }
    % \draw[thick,blue,rounded corners=10pt] (-1.7,1.2) rectangle (1.7,-1.7);
    % \node at (1.2,-1.3) {O};
    % \node (pi) at (-2.5,.5) {$\pi$};
    % \node (phi) at (2.5,-1.) {$\phi_{c}$};

    \node[agent] (a1) {A$_{1}$};
    \node (a2) [right of=a1]  {$\dots$};
    \node[agent] (am) [right of=a2] {A$_{M}$};
    \node[coord] (c) [above of=a2] {Coord};

    \draw[-latex] (a1) to [out=60,in=210] node [sloped,above] {$\vec{\lambda_{1}}$} (c) ;
    \draw[-latex] (c) to [out=-120,in=30] node [sloped,below] {$\vec{\theta}_{1}$} (a1);

    \draw[-latex] (am) to [out=150,in=-60]node [sloped,below] {$\vec{\lambda}_{M}$} (c);
    \draw[-latex] (c) to [out=-30,in=120] node [sloped,above] {$\vec{\theta}_{M}$} (am);

  \end{tikzpicture}
  \caption{Graph representation of Coordinator exchangin with $M$ agents in a \dmpc{} framework.}\label{fig:dmpc_graph}
\end{figure}
